### 2013-02-13 doc/icml2013/evaluation.tex
Added EM Iters as a flag for spectral experts

Describe EM (talk about initialization, number of iterations / stopping
condition).

@@

\paragraph{Datasets}
Describe the Curves dataset.
$x = (t, t^4, t^9)$
$d = b^p$

@@

Dataset 1: visualization ($b = 1, p = 3$)

@@

>>>>

We ran expectation-maximization until the log likelihood converged
$10^-5$. Initialized the entries of $\beta$ with a random Gaussian, $\normal{0}{1}$.

In all our experiments, EM converged.

@@

\paragraph{Datasets}
Describe the Curves dataset.
$x = (1, t, t^4, t^9)$
$d = b^p$

@@

Dataset 1: visualization ($b = 1, p = 3$) (DONE)
Plot for visualization

@@

Table on different settings: 
  (To show that we work comparably or better to EM always)
